% !TEX root = CCBusinessPlan.tex

\chapter{General Company Description}

\section{Company Summary}

Bowtaps is a software development company focused on a complete user experience. The company founded the mobile application Crowd Control. As a start-up company we have a closely connected group of people that have the shared goals of changing how people use mobile applications for the better.

\section{Mission}

Our mission at Bowtaps is to develop innovative mobile software applications to provide solutions to inconveniences that trouble the everyday user. Through the products we create, we aim to change the mobile environment by creating applications with easy-to-use features, intuitive interfaces, and reliable services that our customers can depend on.

\section{Goals}

	\begin{itemize}
	\item Reduce everyday inconvienences through software
	\item Build easy-to-use, well-designed applications
	\item Generate revenue to fund future growth
	\end{itemize}


\section{Keys To Success}

	\begin{itemize}
	\item Establish our presence in the marketplace
	\item Build trust with users through strong customer relations
	\item Utilize the latest features in mobile technology
	\item Apply user feedback to develop improved products
	\item Continue to create innvoative solutions to modern inconveniences
	\end{itemize}

\section{Company History}

Bowtaps was created from an idea of our flagship product Crowd Control.  It spawned out of a competition called the Butterfield Cup.  In May of 2015, when our team took first place with Crowd Control, we realized that we could take our idea from concept to reality.  During the summer of 2015 we attended the Business Accelerator by the Enterprise Institute and hosted by the South Dakota School of Mines and Technology.  From there, we went on to compete in the Student Pitches competition at the Rapid City Innovation Expo and took second place.  We started development on Crowd Control in September of 2015 and since then have been working towards building both a strong company and a solid product.

\section{Milestones}
\begin{center}
\begin{tabular}{|l |l |}
\hline
\multicolumn{1}{|c|}{\textbf{Milestone}} & \multicolumn{1}{c|}{\textbf{Due Date}}\\
\hline
Butterfield Cup Competition & 2015-05-08\\
\hline
Business Accelerator & 2015-06-22\\
\hline
Reserve web domain & 2015-08-18\\
\hline
Innovation Expo & 2015-09-29\\
\hline
SDSM\&T CEO Program & 2015-12-05\\
\hline
SD Governor's Giant Vision submission & 2016-02-19\\
\hline
File for LLC & 2016-02-26\\
\hline
Alpha testing for Crowd Control & 2016-03-04\\
\hline
Senior Design Fair & 2016-04-19\\
\hline
Beta testing for Crowd Control & 2016-04-26\\
\hline
Crowd Control Release & 2016-08-01\\
\hline
Crowd Control Feature Update & 2016-10-01\\
\hline
Crowd Control Feature Update & 2016-12-01\\
\hline
\end{tabular}
\end{center}
