% !TEX root = CCBusinessPlan.tex


\chapter{Executive Summary}


Bowtaps is a software development company focused on technological innovation. The company aims to provide mobile solutions that alleviate the stresses of modern life. Through innovation in mobile technology, we can create products that will change the way users go about their daily lives.

 Our flagship product is Crowd Control, a mobile application designed to ease the experience of going out. Crowd Control will accomplish this tough integrated group messaging, GPS mapping and group status updates.
 
Currently there is nothing on the market that meets the same criteria that we are implementing. As we will cover, other apps that already exist only implement one key feature of our app, while Crowd Control has the functionality of all its competitors in one place.
 
Our initial market entry plan is to keep the app free to download in order to lower the barrier of entry for users. Sponsored ads, or “suggestions” will be our primary revenue source. Suggestions are a way to give users ideas of for possible events for their group to attend around them.

Ad space will be sold based on a the population of users in the area. With this being said initially there is not a steady price for ad space and will be calculated based on how the user population grows in the area.

We chose to distribute the app for free to have an easier entry to the market. With Crowd Control being free, it allows for more users to obtain and use the app without having to make an in store purchase. It is possible to increase the price from free to something under \$5.00, depending on the growth of the userbase.

In the app market, especially as a start-up company, the entry into the market is crucial. With no other apps to back us with funding, we need to have our user base grow as fast as possible. When the user base is established it will allow us to decide on possible additions to the app, as well as making pricing rates for advertisers easier to calculate. 

As our user base dictates our finances, our financial plan is at a minimum, for funding the development and initial launch of Crowd Control. The server we are using allows us to keep a pricing plan that is free for smaller amounts of usage, then increases as our usage increases. Pricing increases as our usage exceeds one million unique server requests per month, which is ideal for development, but must be maintained in release.

As this document is a precursor to the app release, items in this document are subject to change.




