% !TEX root = CCBusinessPlan.tex


\chapter{General Company Description}


\section{Company Summary}

BowTaps is a software development company focused on a complete user experience. The company founded the mobile application Crowd Control. As a start-up company we have a close connected group of people that have the shared goals of changing how people use mobile applications for the better

\section{Mission}

Our mission at BowTaps is to develop innovative mobile software applications to provide solutions to inconveniences that trouble the everyday user. With our software we plan on changing the mobile environment by creating applications with easy to use and  intuitive interfaces with reliable services for everyday use.

\section{Objectives}

	\begin{itemize}
	\item Generate revenue
	\item Provide users with value added user-friendly applications
	\end{itemize}


\section{Keys To Success}

	\begin{itemize}
	\item High quality and innovative development skills
	\item Strategic planning 
	\item Rapidly gaining users and maintaining growth 
	\item Reliable technology
	\end{itemize}

\section{Company History}

Our team consists of five employees made up of undergraduate Computer Science students from the South Dakota School of Mines \& Technologies. 

\textbf{Charles Bonn:} Charles Bonn founded the idea of a mobile application that would help locate and manage groups of people; this idea grew into Crowd Control. As the CEO and Project Manager, Charles acts as the intermediary between BowTaps and the Community of app development. On the technical side he is working with the server backend and communication of the server and Crowd Control \\
\textbf{Johnathan Ackerman:} Johnathan is designated as our Quality Assurance specialist. He would be responsible for fact-checking the group’s work and ensuring that the project fits within design specifications and complies with coding standards. During development for Crowd Control, he will also contribute as the lead Graphical designer for android and create the android user interface experience.\\
\textbf{Daniel Andrus:} Our Lead Designer, Daniel, is responsible for creating an adaptive and attractive user experience for Crowd Control. He will also be with collaborating with Evan Hammer and Charles Bonn on product and company branding. As development begins he will be working with the iOS user interface experience.\\
\textbf{Evan Hammer:} In charge of Sales and Marketing information, Evan keeps track of and coordinates expense and revenue flow related to the company. Evan also provides a unique and useful perspective on our target demographic with his prior job experience. He will work with local businesses and events both to promote our product and to advertise on our platform. As development begins he will be concentration on creating the backend for iOS. \\
\textbf{Joseph Mowry:} Joseph is in charge of designing the data models supporting Crowd Control. With the database being a key feature he will design and implement key features that will allow Crowd Control to be a versatile and efficient application. As development begins he will be concentrating on the backend of Android development.\\






