% !TEX root = CCBusinessPlan.tex


\chapter{Strategy and Implementation Summary}

After our product is thoroughly tested, we plan host an early release at an existing local event. This will allow us to promote Crowd Control to a large user base, as well as network with the existing businesses to help bring our users and them together, to benefit both parties.

\section{Market Strategy}
As there are many alternatives to our product, our primary mission is to show that Crowd Control can be the all-in-one package that users will need. Since no apps currently encapsulate all the things that our product will, it is important for us to play to our strengths.

We will be working closely with local businesses to help promote events and use those events as opportunities to showcase what our app does and why Crowd Control is their next necessary tool when going to these events.

The Rapid City/Black Hills area is perfect for an initial release, as it has a large tourist influx and hosts many local events in and around the hills. The spaciousness of the area is another opportunity to showcase our GPS location features, and help validate that, if this app is in a larger city, it will scale well.

It is critical to keep the relationship with businesses strong, as this is one of the features that will set us apart from our competitors. Many different services that do focus on event management, don’t promote businesses.

\section{Sales Strategy}

Crowd Control’s largest barrier to entry (as is with most mobile applications), is the price; our app must remain free to retain the largest amount of users, as most people will not download an app if they have to pay for it beforehand.

Since Crowd Control will be free, revenue will come from the connection we have with businesses and different event coordinators. Our in-app suggestions to the user's (sponsored by businesses) will be the primary source of revenue, as this will connect our users with our sponsors.


\subsection{Price Setting}
Price setting depends on our user base. With locations “sponsoring” add space it depends on how many user are in the area. The more users in the area, the greater the cost.

This area will be more easily understood as Crowd Control grows but with the initial product being free and advertising being dependent on user base in the area, it is hard to predict at the moment.






