% !TEX root = CCBusinessPlan.tex


\chapter{Executive Summary}

Bowtaps is a software development company focused on technological innovation. We aim to provide mobile solutions that alleviate the stresses of modern life. Our passionate and experienced developers strive to create products that will change the way users go about their daily lives. \\

 Our flagship product is Crowd Control, a mobile application designed to ease the experience of going out. Crowd Control will accomplish this through integrated group messaging, GPS mapping, and group status updates. It will provide users with a reliable and easy way to track their friends and fellow users at events of any kind, while providing local businesses a platform to showcase their venue. \\
 
 Currently there is nothing on the market that meets the same criteria that we are implementing. As we will cover, other apps that already exist only implement one key feature of our app, while Crowd Control has the functionality of all its competitors in one place.\\
 
Our initial market entry plan is to keep the app free to download in order to lower the barrier of entry for users. Sponsored ads, or “suggestions” will be our primary revenue source. Suggestions are a way to give users ideas for possible events for their group to attend in their area.\\

Ad space will be sold based on the population of users in the area. Since this price is essentially demand-based, price of advertisement will be calculated based on how the user population grows in the area. As more people use Crowd Control, the price of the ad space will increase as it will be a more desirable platform. It is important to note that our ads are not traditional banner ads; rather, they are sponsored event suggestions, made available to users that are searching for events in their area. We believe this is especially attractive to users as it is unobtrusive, and fits with the functionality of the app.\\

We choose to distribute the app for free, so that it has an easier entry to the market. With Crowd Control being free, it allows for more users to obtain and use the app without having to make an in-store purchase for a product that they are not familiar with. Though the price of the app will stay free, premium cosmetic enhancements and increased group sizes can be added at a small cost to the user. The increase in group sizes can be either temporary or permanent, depending on the user's needs.\\

In the app market, the entry into the marketplace is crucial, especially as a start-up company. Currently, without other Bowtaps apps released to back us with funding, we need to have our user base grow as fast as possible. A strong entry into the marketplace can help fuel our development, and our ability to expand with add-on features. This will also allow us to take on more projects, further widening our potential revenue. \\

As our user base dictates our finances, our financial plan is to keep all costs at a minimum for funding the development and initial launch of Crowd Control. The server we are using allows us to keep a pricing plan that is free for smaller amounts of usage, then increases as our usage increases. Pricing increases as our usage exceeds one million unique server requests per month, which is ideal for development, but must be maintained in the release phase. Additionally, Crowd Control was programmed in such a way that, if needed, we can transition from our current back-end service relatively easily.
