% !TEX root = CCBusinessPlan.tex


\chapter{General Company Description}


\section{Company Summary}

Bowtaps is a software development company focused on a complete user experience. The company founded the mobile application Crowd Control. As a start-up company we have a close connected group of people that have the shared goals of changing how people use mobile applications for the better

\section{Mission}

Our mission at Bowtaps is to develop innovative mobile software applications to provide solutions to inconveniences that trouble the everyday user. With our software we plan on changing the mobile environment by creating applications with easy to use and  intuitive interfaces with reliable services for everyday use.

\section{Objectives}

	\begin{itemize}
	\item Reduce Inconvieneces
	\item Provide users with value added user-friendly applications
	\end{itemize}


\section{Keys To Success}

	\begin{itemize}
	\item High quality and innovative development skills
	\item Strategic planning 
	\item Rapidly gaining users and maintaining growth 
	\item Reliable technology
	\end{itemize}

\section{Company History}

Bowtaps was created from an idea of our flagship product Crowd Control.  It spawned out of a competition called the Butterfield Cup.  In May of 2015 our team took first place with Crowd Control, we realized there was that we could take our idea and make it a reality.  During the summer of 2015 we attended the Business Accelerator at South Dakota School of Mines and Technology.  From there we went on to compete in the Student Pitches competition at the Rapid City Innovation Expo and took second place.  We have started development of Crowd Control in September of 2015 and since then have been running strong on development.

\section{Milestone}
\begin{center}
\begin{tabular}{|c | c|}
\hline
Milestone & Due Date\\
\hline
Completed Business Accelerator & Completed \\
\hline
Release & 8/1/2016\\
\hline
\end{tabular}
\end{center}








