\documentclass[11pt]{article}

\usepackage[width=7.0in, height=9.0in, top=1.0in, papersize={8.5in,11in}]{geometry}
\usepackage[pdftex]{graphicx}
%\usepackage{datetime}
\usepackage{anyfontsize}
\usepackage{t1enc}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{framed}
\usepackage{pdfpages}
\usepackage{listings}
\lstset{language=C}

\lstset{language=python,frame=ltrb,framesep=5pt,basicstyle=\normalsize,
 keywordstyle=\ttfamily\color{DarkRed},
%morecomment=[n][\textbf]{In\ [}{]\:},
%morecomment=[n][\textbf]{Out\ [}{]\:},
morecomment=[s][\color{blue}]{In\ [}{]\:},
morecomment=[s][\color{red}]{Out[}{]\:},
identifierstyle=\ttfamily\color{DarkBlue}\bfseries,
commentstyle=\color{DarkGreen},
stringstyle=\ttfamily,
showstringspaces=false,tabsize = 3}


\lstdefinelanguage{shell} {
commentstyle = \color{black},
keywordstyle = \color{black},
stringstyle = \color{black},
identifierstyle = \color{black},
morecomment=[s][\color{blue}]{In\ [}{]\:},
morecomment=[s][\color{red}]{Out[}{]\:},
 }

\pagestyle{empty}

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

%\usepackage{sectsty}
%\sectionfont{\MakeUppercase\rmfamily\hrule}

\usepackage{titlesec}
\titleformat{\section}
{\normalfont\large\bfseries}{}{0em}{\hrule height 1pt\vspace{2pt}}[\hrule height 0.2pt]

\begin{document}

{\fontsize{16}{16}\selectfont Sprint Report \#1}

\section*{Team Overview}

\subsection*{Name}
Crowd Control
\subsection*{Members}
Johnathan Ackerman, Daniel Andrus, Charles Bonn, Evan Hammer, Joseph Mowry
\subsection*{Project Title}
Crowd Control Group Management Mobile Application
\subsection*{Company}
Bowtaps

\section*{Customer Overview}

\subsection*{Customer Description}
Bowtaps is a start up company based out of Rapid City, SD. Bowtaps plans on having their initial market presence with the mobile application Crowd Control.

\subsection*{Customer Problem}
The design, creation, and marketing of the mobile application Crowd Control along with the creation of the company Bowtaps.

\subsection*{Customer}

	\begin{itemize}
		\item GPS mapping of Members in the group
		\item Integrated group messaging
		\item Group management features ( add/remove members )
		\item Intuitive UI
		\item Product testing
		\item Marketing plan and strategies
		\item Business plan
		\item End-user Documentation
	\end{itemize}
\section*{Project Overview}
The creation of Crowd Control, a mobile application on Android and iOS platforms for group management.

\subsection*{Phase 1}
The design of the database and the basic design of the user interface.

\section*{Project Environment}

\subsection*{Project Boundaries}
	\begin{itemize}
	\item Crowd Control will be a free app available for download on the Android and iOS marketplaces.
	\item The product will be coded in Java ( Android ) , swift ( iOS ), and parse (back-end server).
	\item Source code will be kept in a private GitHub repository.
	\item Crowd Control will be planned on release by summer of 2016.
	\end{itemize}
	
\subsection*{Project Context}
	\begin{itemize}
	\item There will be 2 versions of the application ( one for iOS and one for Android )
	\item Crowd Control will access a parse server
	\item Crowd Control will access GPS information
	\end{itemize}

\section*{Deliverables}

\subsection*{Phase 1}
Deliverables will be UX design, database design and implementation.

\section*{Backlog}

\subsection*{Phase 1}

	
	\begin{itemize}
	\item Design UX
		\begin{enumerate}
		\item Create groups
		\item Leave groups
		\item Group messaging
		\item Start page
		\end{enumerate}
	\item Database
		\begin{enumerate}
		\item Design database schema
		\item Implement database on Parse
		\end{enumerate}
	\item Design application layers ( MVC )
	\item Set up GitHub repository
	\end{itemize}
	
\section*{Sprint Report}

\subsection*{Work for this sprint included:}
	\begin{itemize}
	\item Designs for Create Group page
	\item Design for Leave Group page
	\item Design for Group Messaging page
	\item Design for Start Page
	\item Design for Database Schema
	\item Database implementation
	\item Git Repository Initialization
	\end{itemize}

\end{document}